%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Shivam Mittal} \\ \vspace{1pt}
    \small +91 8851660028 $|$ \href{mailto:shivammittal2124@gmail.com}{\underline{shivammittal2124@gmail.com}} $|$
    \href{https://www.linkedin.com/in/shivammittal21/}{\underline{www.linkedin.com/in/shivammittal21/}} $|$
    \href{https://github.com/CodeGeek04}{\underline{github.com/CodeGeek04}}
\end{center}


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Delhi Technological University}{Delhi, India}
      {B.Tech. in Computer Science}{2021 - 2025}
  \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Developer}{May 2025 - September 2025}
      {Morphle Labs}{Gurgaon, India}
      \resumeItemListStart
        \resumeItem{Engineered scalable medical automation solutions, reducing manual workflows by 60\% and improving operational efficiency.}
        \resumeItem{Developed advanced image processing frameworks for enhanced diagnostic capabilities and data analysis.}
        \resumeItem{Implemented developer productivity tools, streamlining engineering workflows and accelerating project delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {AI Innovation Specialist}{April 2024 - May 2025}
      {IgniteTech}{Remote}
      \resumeItemListStart
        \resumeItem{Led full-stack development for MyPersonas.ai and Eloquens.ai, contributing to a 20\% increase in customer retention and preventing \$2M in potential revenue loss.}
        \resumeItem{Modernized legacy codebases across multiple platforms, enhancing system stability and optimizing application performance by 15\%.}
        \resumeItem{Collaborated with cross-functional teams to translate complex customer problems into robust technical solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{June 2024 - August 2024}
      {Clausewise}{Remote}
      \resumeItemListStart
        \resumeItem{Developed and integrated advanced AI and NLP features into a contract management platform, improving document processing efficiency by 25\%.}
        \resumeItem{Contributed to building a robust contract management platform, ensuring data integrity and system reliability for legal operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{April 2024 - August 2024}
      {Homeland Connect}{Remote}
      \resumeItemListStart
        \resumeItem{Managed and optimized systems handling 50,000+ tasks per project for a task management system, ensuring high availability and performance.}
        \resumeItem{Developed and maintained responsive mobile application components, delivering a seamless user experience across platforms.}
        \resumeItem{Built a robust platform processing over 10,000 daily inputs with 99.9\% uptime, demonstrating expertise in scalable backend services.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Linklee.in - Custom Link Management Platform} $|$ \emph{Next.js, PostgreSQL, Redis, Cloudflare}}{2024}
          \resumeItemListStart
            \resumeItem{Architected and deployed a full-stack link management platform, handling 10,000+ daily inputs with 99.9\% uptime.}
            \resumeItem{Implemented custom subdomain functionality using Next.js, PostgreSQL, and Redis, enhancing user experience and platform flexibility.}
            \resumeItem{Optimized data retrieval and caching strategies with Redis and Cloudflare, significantly improving application performance and scalability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Python, JavaScript, Go, Java, C/C++, AppScript} \\
     \textbf{Frameworks}{: Node.js, React, Next.js, FastAPI, Express.js} \\
     \textbf{Developer Tools}{: Docker, Kubernetes, AWS, PostgreSQL, Redis, Git, CI/CD, Prisma ORM} \\
     \textbf{Libraries}{: PyTorch, Hugging Face, LangChain, Computer Vision}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}